Fleet Definitions

### 2021-03-01 docs/GBFleetDefinitions.Rmd
update rmd with clustering plots

gearData <- readRDS(file=here::here("data","gearLandingsBySpecies.rds"))
gearTypes <- unique(gearData$data$NEGEAR2)
numGearsGB <- length(gearTypes)
```
There are a total of `r numGears` unique NEGEAR2 codes (found in the cfdbs.gear table). However on Georges Bank not all of these fishing gears are used. A subset of `r numGearsGB` gear types are used. A list of these codes follow

@@

GBCodes <- gearCodes %>% dplyr::filter(NEGEAR2 %in% sprintf("%02d",gearTypes)) %>% 
  dplyr::select(-NEGEAR,-NAFOGEAR,-NAFOGRNM)

@@

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on all gears used in the Georges Bank Ecological Production unit defined by statistical areas"}
knitr::include_graphics("figures/dendrogram1.png")
```

>>>>

```
There are a total of `r numGears` unique NEGEAR2 codes (found in the cfdbs.gear table). However on Georges Bank not all of these fishing gears are used. A subset of 45 gear types are used. All gear codes:

@@

GBCodes <- gearCodes %>% 
  dplyr::select(-NEGEAR,-NAFOGEAR,-NAFOGRNM)

@@

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on all gear types used in the Georges Bank Ecological Production unit as defined by statistical areas",eval=T,echo=F}
knitr::include_graphics("figures/dendrogram1.png")
```
Note: Low values of the agglomerative coefficient indicate tight clustering of gears types. Larger values indicate less well formed clusters.

### Alternative approach

Details to follow:

```{r dendro2,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on a subset of gear types in the Georges Bank Ecological Production unit as defined by statistical areas. Gear types were selected based on their contribution to 99% of landings",eval=T,echo=F}
knitr::include_graphics("figures/dendrogram2.png")
```
